### 2023-12-24 documentation/thesis/thesis_document.tex
more thesis

\begin{itemize}
\tightlist
\item
  sync impulse =\textgreater{} 1 mastersensor als taktqelle
\item
  interene mittelung und speichern der werte im buffer ringubber welcher
  bei jedem sync impuls neu belegt wird
\item
  ringbuffer
\end{itemize}

\%\%Unified\_sensor\_firmware\_multi\_sensor\_synchronisation\_procedure.drawio.png\%\%

\ref{Unified_sensor_firmware_multi_sensor_synchronisation_procedure.drawio.png}

@@

>>>>

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Multi_sensor_synchronisation_wiring_example.png}
\caption{Multi sensor synchronisation wiring example
\label{Multi_sensor_synchronisation_wiring_example.png}}
\end{figure}

One problem with the use of several sensors on one readout host \gls{pc}
is that the measurements may drift over time. On the one hand, \gls{usb}
latencies can occur. This can occur due to various factors, including
device drivers, data transfer speed and system resources. High-quality
\gls{usb} devices and modern drivers often minimise latencies.
Nevertheless, complex data processing tasks and overloaded \gls{usb}
ports can lead to delays.

The other issue is sending the trigger signal from the readout
software\ref{software-readout-framework}. Here too, unpredictable
latencies can occur, depending on which other tasks are also executed on
this port.

In order to enable the most stable possible synchronisation between
several sensors, an option has already been created to establish an
electrical connection between sensors. This is used together with the
firmware to synchronise the readout intervals. The
schematic\ref{Multi_sensor_synchronisation_wiring_example.png} shows how
several sensors must be wired together in order to implement this form
of synchronisation.

\begin{figure}
\centering
\includegraphics{./generated_images/border_Unified_sensor_firmware_multi_sensor_synchronisation_procedure.png}
\caption{Unified sensor firmware multi sensor synchronisation procedure
\label{Unified_sensor_firmware_multi_sensor_synchronisation_procedure.png}}
\end{figure}

Once the hardware has been prepared, the task of the firmware of the
various sensors is to find a common synchronisation clock. To do this,
the \passthrough{\lstinline!register irq on sync pin!} is overwritten.
To set one \passthrough{\lstinline!primary!} and several
\passthrough{\lstinline!secondary!} sensors, each sensor waits for an
intial pulse on the
sync-pin\ref{Unified_sensor_firmware_multi_sensor_synchronisation_procedure.png}.
Each sensor starts a random timer beforehand, which sends a pulse on the
sync line. All others receive this and switch to
\passthrough{\lstinline!secondary!} mode and synchronise the
measurements based on each sync pulse received. Since the presumed
\passthrough{\lstinline!primary!} sensor cannot register its own sync
pulse (because the pin is switched to output), there is a timeout
\passthrough{\lstinline!got pulse within 1000ms!} and this becomes the
\passthrough{\lstinline!primary!} sensor. This means that in a chain of
sensors there is exactly one \passthrough{\lstinline!primary!} and many
\passthrough{\lstinline!secondary!} sensors. In single-sensor operation,
this automatically jumps to \passthrough{\lstinline!primary!} sensor
operation through the
\passthrough{\lstinline!got impulse within 1000ms!} query. The
synchronisation status can be queried via the user
interface\ref{communication-interface} using the
\passthrough{\lstinline!opmode!}\ref{Query_opmode_using_(+cli).png}
command. An important aspect of the implementation here was that there
is no numbering or sequence of the individual sensors. This means that
for the subsequent readout of the measurements, it is only important
that they are taken at the same interval across all sensors. The sensor
differentiation takes place later in the readout
software\ref{software-readout-framework} by using the sensor
identification number.

\begin{figure}
\centering
\includegraphics{./generated_images/border_Query_opmode_using_(+cli).png}
\caption{Query opmode using \gls{cli}
\label{Query_opmode_using_(+cli).png}}
\end{figure}
